First Order Alternation

### 2018-05-25 quantifiers/draft.tex
ok

>>>>

\subsection{Configuration-based Semantics}

We give a low-level operational semantics of automata, in terms of
sets of configurations, with a conjunctive meaning. A (possibly
infinite) set $C$ of configurations is also called a
\emph{cube}. Intuitively, an automaton $\A$ is in a cube $C$ if it is
simultaneously in all configurations $q(d_1, \ldots, d_{\#(q)})$ from
$C$. A positive sentence $\phi$ containing at least one occurrence of
a predicate, defines a (possibly infinite) set of cubes $\sem{\phi}$,
defined next.

A \emph{context} $q[x_1,\ldots,x_k] = q(\delta_1, \ldots,
\delta_{\#(q)})$ is a configuration in which one or more variables may
occur, i.e. $\delta_i \in \Data^\I \cup \set{x_1,\ldots,x_k}$, for all
$i \in [\#(q)]$. For a set of data values $D \subseteq \Data^\I$, we
let $q[x_1,\ldots,x_{i-1},D,x_{i+1}, \ldots, x_k] =
\{q[x_1,\ldots,x_{i-1},d,x_{i+1},\ldots,x_k] \mid d \in D\}$ be a set
of contexts. Observe that $q[D]$ is a cube, when $k=1$.
